\proglang{EpiCompare}: Working title

### 2020-04-30 jss/jss-article-rnw/chapters/ch3-time-free.Rnw
added comments relative to the outline of the paper

>>>>

\ben{My original notes for this section note: ``Ternary plots (pitch from Shannon’s thesis) - being useful to assess. `Peak shows corresponds to the same event in the time analysis' (maybe?)''. I don't necessarily think this section perfectly does that - so I'm open to having it include that or just deciding this is better.}
